---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE, 
                      fig.width = 10, fig.height = 6, out.width = "100%")

```

```{css}
body {
  font-family: Helvetica, sans-serif;
  background-color: #f9f9f9;
  color: #000000;
  margin: 0 auto;
  max-width: 900px;
  padding: 20px;
}

h2 {
  color: #1a6b1a;
  background-color: #e8f5e8;
  text-align: center;
  padding: 12px 0;
  border-radius: 6px;
  letter-spacing: 1px;
}

p {
  font-size: 16px;
  line-height: 1.8;
  color: #000000;
}

.summary-box {
  background-color: #e8f5e8;
  border-left: 6px solid #1a6b1a;
  padding: 14px 24px;
  margin: 24px 0;
  border-radius: 6px;
  font-size: 16px;
  color: #000000;
}

.summary-box strong {
  color: #1a6b1a;
}

.chart-caption {
  text-align: center;
  font-size: 13px;
  color: #555555;
  margin-top: -10px;
  margin-bottom: 20px;
  font-style: italic;
}

hr {
  border: none;
  border-top: 2px solid #c8e6c8;
  margin: 30px 0;
}
```



```{r}
library(tidyverse)

# Reading the data directly from our Google spreadsheet
logged_data <-"https://docs.google.com/spreadsheets/d/e/2PACX-1vT1y6xJgFjjSg3ALmUeJF7VVYIYere3DmdHjrHMiBYq8eDwxxjT8840UPbXw9RYRtpLFsQsHC8yQhG2/pub?output=csv"

# Creating a new data frame for our function
latest_data <- read_csv(logged_data) %>%
  # Renaming the variables in the spreadsheet
  rename(time_stamp = 1,
         day_and_time = 2,
         primary_focus = 3,
         muscle_group = 4,
         session_time = 5,
         no_of_excercises = 6,
         session_hard = 7,
         session_feel = 8,
         notes = 9)

# Computing the summary values to put the code inline
excerise_time <- max(latest_data$no_of_excercises)
total_sessions <- nrow(latest_data)
average_session <- round(mean(latest_data$session_time), 2)
most_common_training <- names(which.max(table(latest_data$primary_focus)))
common_training_amount <- max(table(latest_data$primary_focus))

# Filter to only the most common training type sessions
strength_sessions <- latest_data %>%
  filter(primary_focus == most_common_training)

# Find the most common session feel within that group
most_common_feel <- names(which.max(table(strength_sessions$session_feel)))

# Count how many sessions had that most common feel (fully dynamic)
energised_strength <- strength_sessions %>%
  filter(session_feel == most_common_feel) %>%
  nrow()
```


## Tracking Gym Sessions with Training Habits and Session Experience

This report analyses **`r total_sessions`** gym sessions logged by individuals
in Auckland. Each session logs the **type of training a user performs ** in the session, how long the session was, and how the session felt overall to the user.

The average session length for all logs is **`r average_session`** mins per session.

<hr>
```{r}
# First bar chart 
latest_data %>%
  ggplot() +
  geom_bar(aes(x = primary_focus), fill = "lightblue") +
  labs(x = "Type of Training",
       y = "Number of Sessions",
       title = "Number of Sessions by Training Type")

```

The chart above shows , it shows the **relationship between number of sessions and the type of training**. The most common training type was **"`r most_common_training`"**, which had recorded the **highest number of logged sessions at `r common_training_amount`**.  

<hr>
```{r}
# Second bar chart 
latest_data %>%
  ggplot() +
  geom_bar(aes(x = session_feel, fill = primary_focus)) +
  labs(x = "Feeling of Session",
       y = "Number of Sessions",
       fill = "Training Type",
       title = "Session Feel by Training Type",
       subtitle = "Data was recorded in 2026")
```

The second chart above shows **how the respondents feel after completing a workout** based on their preference of the type of training that they did in their gym session. From the **"`r most_common_training`"** group, **`r energised_strength`** sessions were recorded as feeling  **"`r most_common_feel`"** after completing their workout.
